MA_Results

### 2022-05-30 Markdown/Manuscript/Child_RMDs/Doodles.Rmd
first efforts with t2

>>>>

Libraries:
describing and validating input data [@hamilton_matthew_2022_6084467], 
scoring health utility data [@hamilton_matthew_2022_6084824], 
specifying and testing mapping models [@hamilton_matthew_2022_6116701] 
reporting mapping studies [@gao_caroline_2022_6130155].
make predictions with new data using another R package [@matthew_p_hamilton_2021_5646669] that we developed

Programs:
CSP [@hamilton_matthew_2022_6129906]
Predict [@hamilton_matthew_2022_6416330]
Make Fakes [@hamilton_matthew_p_2022_6321821]

Sub-routines:
Ctlg: [@hamilton_matthew_2022_6116385]
SS: [@matthew_p_hamilton_2022_5976988]

Data
results / replication [@DVN/DKDIB0_2021]  
Fake [@DVN/HJXYKQ_2021]

To facilitate appropriate use of the mapping models we developed we created catalogues with detailed information about the performance of all models generated by our study under multiple types of regime (e.g. whether: mean or sampled parameter values are used; minimum and maximum constraints are applied to prediction results; the original R model objects or just tables of model coefficients are used).

### 2022-05-30 Markdown/Manuscript/Child_RMDs/MS_Conclusion.Rmd
first efforts with t2

---
title: "MS_Conclusion"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
`r ifelse(is.na(params$X@conclusion_1L_chr),"",params$X@conclusion_1L_chr)`

>>>>

---
title: "MS_Conclusion"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
`r ifelse(is.na(params$X@conclusion_1L_chr),"",params$X@conclusion_1L_chr)` 
<!-- Standards generalisable, Toolkit less os -->

### 2022-05-30 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
first efforts with t2

<!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
Computational models have become essential tools for health policy development [@Erdemir2020]. Although influential and widely used, these models routinely contain errors [@Radeva2020], are rarely adequately validated [@Ghabri2019], can be difficult to reproduce [@Jalali2021; @McManus2019; @Bermejo2017] and are likely to be infrequently updated or revised [@Sampson2017]. To help address these issues, there is growing support for greater use of open source health economics models (OSHEMs) that grant liberal permissions to access and re-use model source code [@Pouwels2022]. However, to date actual implementations of OSHEMs are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022]. Barriers to adoption include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019]. As many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations may also limit the uptake of OSHEMs [@Feenstra2022].

There is also a need to develop good practice recommendations for OSHEMs [@Sampson2019]. Adherence to explicit standards is as essential requirement for quality health economic model implementation [@Erdemir2020], but current guidance for OSHEMs is scarce and piecemeal. Guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on documenting models but notably not on the sharing of model code and data. More recent and more general modelling guidance [@Erdemir2020] recommends the sharing of code and data through platforms such as GitHub [@github2007] and Zenodo [@Zenodo2013] and the use of version control systems such as Git [@git20XX]. A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019].

>>>>

<!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
Health economic computational models have become essential tools for health policy development [@dakin2015influence; @Erdemir2020]. Although influential and widely used, these models routinely contain errors [@Radeva2020], are rarely adequately validated [@Ghabri2019], can be difficult to reproduce [@Jalali2021; @McManus2019; @Bermejo2017] and are likely to be infrequently updated or revised [@Sampson2017]. To help address these issues, there is growing support for greater use of open source health economic models (OSHEMs) that grant liberal permissions to access and re-use model source code [@Pouwels2022]. However, to date actual implementations of OSHEMs are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022]. Barriers to adoption include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019]. As many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations may also limit the uptake of OSHEMs [@Feenstra2022].

Better guidance about how to implement OSHEMs is required [@Sampson2019]. Adherence to explicit standards is as essential requirement for modelling in healthcare [@Erdemir2020], but current best practice recommendations for OSHEMs are scarce and piecemeal. Guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on documenting models but notably not on the sharing of model code and data. More recent and more general modelling guidance [@Erdemir2020] recommends the sharing of code and data through platforms such as GitHub [@github2007] and Zenodo [@Zenodo2013] and the use of version control systems such as Git [@git20XX]. A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019].

### 2022-05-30 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
first efforts with t2

<!-- Computational modelling could play an important role in developing policies to improve population mental health but this may require significant changes in the way mental health modelling projects are funded, conceptualised and implemented.  -->

Major mental health reform programs will require the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives. Single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020]. Currently, mental health economic models predominantly address issues relating to the affordability and value for money of individual programs [@RN34] with mental health simulation studies rarely modelling complex systems [@RN73]. Greater use of dynamic systems modelling approaches could provide new insights about inter-dependencies between candidate policies and the evolution of the mental health systems planning context [@Occhipinti2021]. These types of models might also be the basis for developing reference models [@Afzali2013] of mental health systems that are intended for multiple-applications and re-use by different modelling teams.

However, as they are intended for multiple-purposes and because propagation errors may be more likely with more complex models [@Saltelli2019] such models require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022]. The development, validation and maintenance of these more complex models may be simply too onerous a burden for a single modelling team. Developing networks of modellers working on common health conditions [@Sampson2019] and collaborations across multiple modelling teams that include the ability to re-use and extend each others work, can make complex modelling projects more tractable [@Arnold2010]. Similarly, more attention to developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure models are appropriately conceptualised and implemented and improve their practical utility as decision aids [@Zabell2021].

Modelling projects should be resourced to be routinely updated and refined as new evidence emerges and decision contexts change [@Jenkins2021]. There are significant deficits in our understanding of the systems in which mental disorder emerges and is treated [@Fried2020] and longer term project horizons could allow mental health models to progressively improve validity as these gaps are addressed. Currently, the theoretical basis for understanding complex mental health systems is weak [@RN2111]. Strikingly, it remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].  The literature about how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context is underdeveloped [@RN42]. There is insufficient evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].

Open source frameworks have been previously recommended for the development of mental health modelling field [@RN73] but, as with health economics more generally, OSHEMs remain rare. Currently there is only one mental health related model (in Alcohol Use Disorder [@Basu2018]) that is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019]. A Major Depressive Disorder reference model for the United States [@IVIMDD2022] is also being developed as part of the Open Value Initiative [@Jansen2019]. We believe greater support for open source approaches have the potential to provide more transparent, collaborative and sustained approaches to mental health system model development.

@@

# Framework
The framework we have developed to implement readyforwhatsnext consists of specified standards for OSHEMs and tools for meeting those standards.

@@

 - **Transparent**: people can easily see how a model has been implemented and tested;
 - **Iterative**: a model is routinely updated to maintain and improve validity;
 - **Modular**: models and their components can be combined to extend their scope;
 - **Epitomized**: models can be used in multiple decision contexts;
 - **Licensed**: a model and its derivatives are persistently re-usable by other modellers; and
 - **Yielding**: a model can be reliably deployed as a simple and flexible decision aid.

### Transparent Models
A range of tools and practices are available to help make model code and data accessible, citable and comprehensible. The most efficient way to widely disseminate code and data may be to use existing open science infrastructure [@Erdemir2020]. Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each unique item. These repositories are a preferable solution for sharing citable code and data than transitory repositories such as corporate websites or GitHub where items can be deleted or relocated at any time [@sseditors2022]. Zenodo includes tools that automate integration with GitHub, which makes it easy for developers to maintain parallel code repositories - one for disseminating the most up to date development code and the other for archiving citable code releases.

@@

Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019]. The main logic of a program can be made comprehensible to even non-technical users though the use of the common practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphsim [@7181447], where the same command (e.g. "simulate") can be reused to implement different algorithms of the same broad type. Literate programming, where tools like RMarkdown [@xie2018r] are used to render documents that integrate computer code with plain English descriptions of each step in an analysis workflow, can make code easier to follow by both technical and non-technical users.

@@

Adopting semantic versioning [@semver20xx] conventions can be an efficient way to provide users of model code and data with information about the potential importance of an update. For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development. Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention.

Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests. OSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub. These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?, can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).

@@

- **E3: Test data is available to demonstrate generalised model applications**

@@

Licenses may or may not specify that model re-users must give appropriate acknowledgement to model authors. Citation tools can be distributed with each cite individual code or data items to inform re-users of the desired attribution. In R, including a CITATION file in the `inst` directory of a package will enable users of that package to retrieve citation information by running a command of the format `citation("Package Name")` in the R console. More generally, including a CITATION.cff file at the top level of any software item (including those written in R), will enable GitHub and Zenodo repositories hosting that item to include the relevant information in their citation tools. Datasets hosted on Dataverse installations have metadata fields that, once completed by authors, generate citation files for dataset viewers.

@@

- **Y1: Statistical models can be safely and appropriately reused using standardised toolkits** <!-- New, Replaces Old Y1 (now Y2) -->
- **Y2: Non-technical users can configure and run models via simple user-interfaces** <!-- Was Y1 -->

## Toolkits
We have developed a toolkit to help streamline the process of developing OSHEMs that meet the TIMELY standards. The toolkit is comprised of online repositories and software.

### Online Repositories
We have created a GitHub organisation (https://github.com/ready4-dev) for in development model code, a Zenodo community (https://zenodo.org/communities/ready4) for citable archived code and a Dataverse on the Harvard Dataverse for model data (https://dataverse.harvard.edu/dataverse/ready4).

@@

### Software
We have written six R packages to support the development and curation of model code and data. The package ready4 defines the framework's syntax and a model module template class. The ready4class package provides tools for creating self-documenting model module classes, while ready4fun is a toolkit for creating the functions (including methods) that are also self-documenting and written in a consistent house style. Model module classes and functions are bundled into R packages with standardised approaches to quality assurance and documentation using the the ready4pack package. Tools for creating and managing model data are included in the ready4use package, while tools for the analysis and reporting of models are included in the ready4show package. The purpose of each package, the TIMELY standards they support and the third party R packages they depend on are summarised in Table 1. <!-- Autogenerate ref -->

@@

>>>>

<!-- Computational modelling could play an important role in developing policies to improve population mental health but this may require significant changes in the way mental health modelling projects are funded, conceptualised and implemented.  -->
Open source frameworks have been previously recommended for the development of mental health modelling field [@RN73] but, as with health economics more generally, OSHEMs remain rare. Currently there is only one mental health related model (in Alcohol Use Disorder [@Basu2018]) that is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019]. A Major Depressive Disorder reference model for the United States [@IVIMDD2022] is also being developed as part of the Open Value Initiative [@Jansen2019]. Greater use of open source approaches could help improve the scope, validity and usefulness of mental health economic models.

Major mental health reform programs, such as those currently being implemented in Victoria, Australia [@VicRC2021], can involve the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives. Single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020]. Currently, mental health economic models predominantly address issues relating to the affordability and value for money of individual programs [@RN34] with mental health simulation studies rarely modelling complex systems [@RN73]. Systems modelling approaches, that have been recommended for public health economics more generally [@SQUIRES2016588] and for mental health specifically [@Occhipinti2021], could provide greater insight about inter-dependencies between candidate policies and the dynamic nature of the mental health systems planning context. Dynamic systems methods might also be the basis for developing reference models [@Afzali2013] of mental health systems that are intended for multiple-applications and re-use by different modelling teams. However, more complex models may be more prone to error [@Saltelli2019] and models designed for multiple purposes require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].

To retain and improve their utility as decision aids, health economic models require updating and refinement as new evidence emerges and decision contexts change [@Jenkins2021]. There are significant deficits in our understanding of the systems in which mental disorder emerges and is treated [@Fried2020] and longer term project horizons could allow mental health economic models to progressively improve validity as these gaps are addressed. Currently, the theoretical basis for understanding complex mental health systems is weak [@RN2111]. Strikingly, it remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].  The literature about how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context is underdeveloped [@RN42]. There is insufficient evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].

The development, validation and updating of more complex mental health economic models implemented over longer time frames may be too onerous a burden for a single modelling team. Developing networks of modellers working on common health conditions has been recommended as a strategy for improving model validity [@Sampson2019] and a some of us are part of a nascent initiate of this type in mental health [@nmhsmn2022]. Furthermore, collaborations across multiple modelling teams that include the ability to re-use and extend each others work can make complex modelling projects more tractable [@Arnold2010]. <!-- Add ref to NMHSMN in Australia --> Similarly, developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure models are appropriately conceptualised and implemented and improve their practical utility as decision aids [@Zabell2021; @SQUIRES2016588].

@@

# Framework
The framework we have developed to implement readyforwhatsnext specifies standards for OSHEMs and provides tools for meeting those standards.

@@

 - **Transparent**: people can easily see how a model has been implemented and tested;
 - **Iterative**: a model is routinely updated to maintain and improve validity;
 - **Modular**: models and their components can be combined to extend their scope;
 - **Epitomized**: a model and its components can be used in multiple decision contexts;
 - **Licensed**: a model, its components and derivatives are persistently re-usable by other modellers; and
 - **Yielding**: a model can be simply, flexibly and reliably used to inform decision-making.

### Transparent Models
A range of tools and practices are available to help make model code and data accessible, comprehensible and citable. The most efficient way to widely disseminate code and data may be to use existing open science infrastructure [@Erdemir2020]. Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each unique item. These repositories are a preferable solution for sharing citable code and data than transitory repositories such as corporate websites or GitHub where items can be deleted or relocated at any time [@sseditors2022]. Zenodo includes tools that automate integration with GitHub, which makes it easy for developers to maintain parallel code repositories - one for disseminating the most up to date development code and the other for archiving citable code releases.

@@

Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019]. Code can be made easier to follow by using the practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphsim [@7181447], where the same command (e.g. "simulate") can be reused to implement different algorithms of the same type. Programs to implement model analyses can be made comprehensible to even non-technical users though the use of literate programming techniques that use tools like RMarkdown [@xie2018r] to render documents that integrate computer code with plain English descriptions.

@@

Adopting semantic versioning [@semver20xx] conventions can be an efficient way to provide users of model code and data with information about the potential importance of an update. For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development. Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention. 
Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests. OSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub. These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?, can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).

@@

- **E3: Test data is available to demonstrate generalised applications of model code**

@@

Licenses may or may not specify that model re-users must give appropriate acknowledgement to model authors. Citation tools can be distributed with each cite individual code or data items to inform re-users of the desired attribution. In R, including a CITATION file in the `inst` directory of a package will enable users of that package to retrieve citation information by running a command of the format `citation("Package Name")` in the R console [@Salmon2021]. More generally, including a CITATION.cff file at the top level of your code repository will enable GitHub and Zenodo repositories hosting that item to include the relevant information in their citation tools [@Druskat_Citation_File_Format_2021]. Datasets hosted on Dataverse installations have metadata fields that, once completed by authors, generate citation files for dataset viewers.

@@

- **Y1: Statistical models are distributed with validated tools to support their safe and appropriate re-use** <!-- New, Replaces Old Y1 (now Y2) -->
- **Y2: Simple user-interfaces allow non-technical users to configure and run models ** <!-- Was Y1 -->

## Modelling tools
We have developed a toolkit to help streamline the process of developing OSHEMs that meet the TIMELY standards. The toolkit is comprised of online repositories and software.

### Framework repositories <!-- Existing ref -->
We created a GitHub organisation where all framework software source code is stored, documented, version controlled and continuously integrated [@ready4gh2022]. To store citable archived copies of release copies of our software, we created a Zenodo community [@ready4zen2022]. Finally, to manage datasets for use in models developed with the framework, we created a dedicated collection within the Harvard Dataverse  [@ready4dv2022].

### Framework software <!-- Novel ref -->
As a foundation for implementing the framework, we authored a development version R package that defines a novel syntax and a template class for model modules [@ready42022]. To enable the syntax and module template be applied to modelling projects, we then created five additional development version R packages that provide tools for authoring:

- self-documenting model modules [@ready4class2022];

- self-documenting functions (including methods), written in a consistent house style [@ready4fun2022];

- citable, quality assured R packages [@ready4pack2022];

- model datasets [@ready4use2022];

- model analyses and reports [@ready4show2022].

The six R packages, their primary focus, the TIMELY standards they support and the third party packages they depend on are summarised in Table \@ref(tab:cpkgs). When used in conjunction with framework repositories, the six packages currently provide strong support for implementing 17 of the TIMELY standards, weak support for implementing the standards relating to disseminating statistical models (Y1) and user-interface development (Y2) and no support for implementing standard T5 (reporting code coverage). Our future development priorities for these packages include adding functionality so that all 20 TIMELY standards are well supported and to then submit production versions of each package for review by and archiving on the Comprehensive R Archive Network (CRAN) [@CRAN2022].

@@

@@

```{r tab.cap='TIMELY Checklist with utility mapping study worked example', tab.id = 'checklisttb', echo = F, results = 'asis'}
    #  a <- c("TEST1","TEST2")
    # b <- c("\\cite{ready4show2022}", "hjhjhj")
    # tmp <- data.frame(a,b)   
#     kableExtra::kbl(tmp, booktabs = T, escape = F) %>%
#  kableExtra::kable_styling(
#    latex_options = c("striped", "hold_position", "repeat_header")
#    ) %>%  
#   kableExtra::column_spec(2, width = "50em") %>%
# kableExtra::landscape()

checklist_df <- data.frame(Standard = c(paste0("T",1:6, c(" (Publicly archived)",
                                                          " (Documented)",
                                                          " (Simple Syntax)",
                                                          " (Literate programming)",
                                                          " (Code coverage)",
                                                          " (Reproducibility")),
                                        paste0("I",1:4, c(" (Version controlled)",
                                                          " (Semantic versioning)",
                                                          " (Continuous integration)",
                                                          " (Deprecation)")),
                                        paste0("M",1:2, c(" (Decouple code and data)",
                                                          " (Encapsulation)")),
                                        paste0("E",1:3, c(" (Code libraries)",
                                                          " (Inheritance)",
                                                          " (Test data)")),
                                        paste0("L",1:3, c(" (Copyleft for code)",
                                                          " (Liberal, safe data terms)",
                                                          " (Citation tools)")),
                                        paste0("Y",1:2, c(" (Statistical model tools)",
                                                          " (User-interfaces"))),
                           Assessment = rep("Met so well it hurts",20),
                           Description = c("5 libraries [@hamilton_matthew_2022_6084467;@hamilton_matthew_2022_6084824;@hamilton_matthew_2022_6116701;@gao_caroline_2022_6130155;@matthew_p_hamilton_2021_5646669], 3 programs [@hamilton_matthew_2022_6129906;@hamilton_matthew_2022_6416330;@hamilton_matthew_p_2022_6321821], 2 sub-routines [@hamilton_matthew_2022_6116385;@matthew_p_hamilton_2022_5976988] and 2 datasets [@DVN/DKDIB0_2021;@DVN/HJXYKQ_2021]",
# @hamilton_matthew_2022_6084467;@hamilton_matthew_2022_6084824;@hamilton_matthew_2022_6116701;@gao_caroline_2022_6130155;@matthew_p_hamilton_2021_5646669
# Programs:

# 
# Sub-routines:

                                           "XX",
                                           "XX",
                                           "XX",
                                           "XX",
                                           "XX",
                                           "XX",
                                           "XX",
                                           "XX",
                                           "XX",
                                           "XX",
                                           "XX",
                                           "XX",
                                           "XX",
                                           "XX",
                                           "XX",
                                           "XX",
                                           "XX",
                                           "XX",
                                           "XX"))

tb2_nms_chr<-colnames(checklist_df)
checklist_df <- data.frame(checklist_df[,1],
                 rep("&nbsp; &nbsp; &nbsp;",nrow(checklist_df)),
                 checklist_df[,2],
                 rep("&nbsp; &nbsp; &nbsp;",nrow(checklist_df)),
                 checklist_df[,3])
colnames(checklist_df) <- c("","Standard",
                            "Met?", " ",
                            tb2_nms_chr[3])
if(params$X@outp_formats_chr[1] == "Word") {
  checklist_df %>%
    ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
                            use_rdocx_1L_lgl = ifelse(params$X@outp_formats_chr[1]=="Word",T,F),
                            add_to_row_ls = NULL,
                            sanitize_fn = NULL)
  }else{
    checklist_df %>%
    kableExtra::kbl(format = "markdown",
                      #escape = F,
                    caption = knitr::opts_current$get("tab.cap"))
    # df %>%
    #   kableExtra::kbl(booktabs = T,
    #                   caption = knitr::opts_current$get("tab.cap")) %>%
    #   kableExtra::kable_styling(full_width = F) %>%
    #   kableExtra::column_spec(9, width = "17em") %>%
    #   kableExtra::add_header_above(c(" " = 2, "Supports standard" = 6, " "))
    }
```
